Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-08 writing/embedded_meta_learning.tex
Stealing an example from tenenbaum

\section{Meta-mappings}
We propose the challenge of meta-mappings, that is, mappings over tasks. These can take several flavors, including mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior). While the first two categories have been considered in prior work, the latter is more novel. \par
We argue that these meta-mappings are a useful way to think about the flexibility that humans have. For example, suppose an agent knows how to navigate from the airport to downtown. It should be able to adapt to changes of the environment such as street closures. This can be viewed as a change in the task being performed, from navigating through one map to navigating through another. Similarly, a system that is trained to play one level of a video game should be able to adapt to another level where the enemies change color. These again can be seen as two related tasks. We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to use. While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility. In particular, we can use our knowledge of a task to adapt to these type of task alterations zero-shot, that is, without seeing a single example from the new task. \par

>>>>

\section{Meta-mappings}
We propose the challenge of meta-mappings, that is, mappings over tasks. These can take several flavors, including mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior). While the first two categories have been considered in prior work, the latter is more novel. \par
We argue that these meta-mappings are a useful way to think about the flexibility that humans have. For example, suppose an agent knows how to navigate from the airport to downtown. It should be able to adapt to changes of the environment such as street closures. This can be viewed as a change in the task being performed, from navigating through one map to navigating through another. Similarly, a system that is trained to play one level of a video game should be able to adapt to another level where the enemies change color, or a system that learns to play go should be able to adapt to a different board size. These again can be seen as pairs of related tasks. We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose. While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not capture the extent of human flexibility. In particular, we can use our knowledge of a task to adapt to these type of task alterations zero-shot, that is, without seeing a single example from the new task. \par
